---
title: "Cazzo"
author: "LeTwist"
date: "11/6/2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
Load data set
```{r}
activity <- read.csv("activity.csv")
```

Activate graphing libraries
```{r}
library(lattice)
library(ggplot2)
library(plyr)
library(dplyr)
library(lubridate)
library(knitr)
library(markdown)
```

Look at variables
```{r}
head(activity)
```

Transform variables to factors
```{r}
activity <- within(activity, {dateFAC = as.factor(date)})
activity <- within(activity,{intervalFAC = as.factor(interval)})
```

Make sure that the data set does not include NA values
```{r}
actComp <- activity[complete.cases(activity),]
```

View NA-less data set
```{r}
head(actComp)
```

Make a histogram of the total number of steps taken each day
```{r}
totals <- aggregate(steps ~ dateFAC, actComp, sum)
plot1 <- histogram(dateFAC~steps,data = totals)
```

View the histogram of total steps by day
```{r}
plot1
```

Find the mean and median number of steps taken each day
```{r}
means <- aggregate(steps ~ dateFAC, actComp, mean)
medians <- aggregate(steps~dateFAC, actComp, median)
```

View the mean data
```{r}
head(means)
```
View the median data
```{r}
head(medians)
```

Time series plot of the average number of steps taken
```{r}
series <- aggregate(steps~interval,actComp,mean)
plot2 <- plot(series$interval,series$steps, type = "l")
```

The 5-minute interval that, on average, contains the maximum number of steps
```{r}
dim(series)
```

```{r}
max_steps <- max(series$steps)
        for(i in 1:288){
        if (series$steps[i]==max_steps)
                intervalMax <- series$interval[i]
        }
intervalMax
```

Code to describe and show a strategy for imputing missing data
```{r}
missing <- is.na(activity$steps)
table(missing)

fill.value <- function(steps, interval) {
    filled <- NA
    if (!is.na(steps)) 
        filled <- c(steps) else filled <- (series[series$interval == interval, "steps"])
    return(filled)
}
filled.data <- activity
filled.data$steps <- mapply(fill.value, filled.data$steps, filled.data$interval)

head(filled.data)
```
Histogram of the total number of steps taken each day after missing values are imputed
```{r}
imputedTotals <- aggregate(steps ~ dateFAC, filled.data, sum)
histogram(dateFAC~steps,data = totals)
```

Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends
```{r}
weekday.or.weekend <- function(dateFAC) {
    day <- weekdays(dateFAC)
    if (day %in% c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")) 
        return("weekday") else if (day %in% c("Saturday", "Sunday")) 
        return("weekend") else stop("invalid date")
}
filled.data$dateFAC <- as.Date(filled.data$dateFAC)
filled.data$day <- sapply(filled.data$dateFAC, FUN = weekday.or.weekend)

averages <- aggregate(steps ~ interval + day, data = filled.data, mean)
ggplot(averages, aes(interval, steps)) + geom_line() + facet_grid(day ~ .) + 
    xlab("5-minute interval") + ylab("Number of steps")
```